Curve counting in genus one: elliptic singularities {\it \&} relative geometry

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$  of centrally aligned curves is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification. The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$ and a contraction
\[
\widetilde{\mathcal C}_S\to \overline{\mathcal C}_S,
\]
where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}. The number of branches is equal to the sum of the number of vertices \tred{of $\widetilde{\sqC}$} which lie on the circle of radius $\delta$ \sout{and the number of edges which are split by the same circle}. This data uniquely determines the singularity.

>>>>

The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$  of centrally aligned curves is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification. The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$ and a contraction
\[
\widetilde{\mathcal C}_S\to \overline{\mathcal C}_S,
\]
where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}. The number of branches is equal to the sum of the number of vertices of $\widetilde{\sqC}$ which lie on the circle of radius $\delta$. This data uniquely determines the singularity.
